---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# unbiasr

MMM Lab@USC

<!-- badges: start -->
<!-- badges: end -->

## Installation

You can install the development version of unbiasr from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("mmm-usc/unbiasr")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(unbiasr)
## Toy example from Millsap & Kwok (2004, doi: 10.1037/1082-989X.9.1.93)
PartInv(
    propsel = .25,
    alpha_r = 0.5,
    alpha_f = 0,
    psi_r = 1,
    lambda_r = c(.3, .5, .9, .7),
    nu_r = c(.225, .025, .010, .240),
    nu_f = c(.225, -.05, .240, -.025),
    Theta_r = diag(.96, 4)
)
```

## Shiny Application

Browser version: https://mmmlabusc.shinyapps.io/partinvshinyui/

Or call `unbiasr::launch()` in R.

## References

Millsap, R. E., & Kwok, O.-M. (2004). Evaluating the impact of partial factorial invariance on selection in two populations. *Psychological Methods, 9*(1), 93–115. https://doi.org/10.1037/1082-989X.9.1.93

Lai, M. H. C., Kwok, O., Yoon, M., & Hsiao, Y.-Y. (2017). Understanding the impact of partial factorial invariance on selection accuracy: An R script. *Structural Equation Modeling: A Multidisciplinary Journal, 24*(5), 783–799. https://doi.org/10.1080/10705511.2017.1318703

Lai, M. H. C., & Zhang, Y. (2022). Classification accuracy of multidimensional tests: Quantifying the impact of noninvariance. *Structural Equation Modeling: A Multidisciplinary Journal.* Advance online publication. https://doi.org/10.1080/10705511.2021.1977936

The development of this package is supported by the U.S. Army Research Institute for the Behavioral and Social Sciences (ARI) under Grant W911NF2010282. The views, opinions, and/or findings contained in this report (paper) are those of the authors and shall not be construed as an official Department of the Army position, policy, or decision, unless so designated by other documents.
