---
title: "Applied examples"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Applied examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE, warning=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
#knitr::opts_knit$set(upload.fun = image_uri)
```

```{r setup, warning=FALSE, message=FALSE}
library(PartInvShinyUI)
library(lavaan)
```
\newcommand{\SR}{\text{SR}}
\newcommand{\CAI}{\text{CAI}}
\newcommand{\SE}{\text{SE}}
\newcommand{\SP}{\text{SP}}
\newcommand{\PS}{\text{PS}}
\newcommand{\TP}{\text{TP}}
\newcommand{\FN}{\text{FN}}
\newcommand{\FP}{\text{FP}}
\newcommand{\TN}{\text{TN}}
\newcommand{\sfi}{\text{sfi}}
\newcommand{\pfi}{\text{pfi}}
\newcommand{\ef}{\text{Ef}}
\newcommand{\r}{\text{r}}
\newcommand{\f}{\text{f}}
\newcommand{\rr}{\text{r-Ef}}
\newcommand{\h}{\text{h}}
\newcommand{\ov}{\overline}

## Classification Accuracy Indices: Formulas and Notation

### Classification Accuracy Index (CAI)

- Proportion Selected: $\PS=\text{P(TP)}+\text{P(FP)}$

- Success Ratio: $\SP=\dfrac{\text{P(TP)}}{\text{P(TP)}+\text{P(FP)}}$

- Sensitivity: $\SE=\dfrac{\text{P(TP)}}{\text{P(TP)}+\text{P(FN)}}$

- Specificity: $\SP=\dfrac{\text{P(TN)}}{\text{P(TN)}+\text{P(FP)}}$

Unless otherwise indicated, we will assume that the full item set (length J) is
used and that partial factorial invariance (PFI) holds. 

If strict factorial invariance (SFI) holds, this will be denoted as $\CAI_{\sfi}$, e.g., $\SE_{\sfi}$ for SE under SFI.

A CAI computed on an item set excluding item $j \in \{1,\ldots,J\}$ is denoted $\CAI^{|j}$, e.g., $\SE^{|2}$ if SE is computed on the item set excluding the second item.  

### Aggregate Classification Accuracy Index $\left(\ov{\CAI}\right)$

- Aggregate PS: $\ov{\PS}  = \TP_{r}\times p_r + \TP_{f}\times (1-p_r) + \FP_{r}\times p_r + \FP_{f}\times (1-p_r)$

- Aggregate SR: $\ov{\SR} = \dfrac{\TP_{r}\times p_r + \TP_{f}\times (1-p_r)}{\TP_{r}\times p_r + \TP_{f}\times (1-p_r) + \FP_{r}\times p_r + \FP_{f}\times (1-p_r)}$
 
- Aggregate SE: $\ov{\SE} = \dfrac{\TP_{r}\times p_r + \TP_{f}\times (1-p_r)}{\TP_{r}\times p_r + \TP_{f}\times (1-p_r) + \FN_{r}\times p_r + \FN_{f}\times (1-p_r)}$

- Aggregate SP: $\ov{\SP} = \dfrac{\TN_{r}\times p_r + \TN_{f}\times (1-p_r)}{\TN_{r}\times p_r + \TN_{f}\times (1-p_r) + \FP_{r}\times p_r + \FP_{f}\times (1-p_r)}$

$\ov{\CAI}$ is only computed for the partial invariance case (hence, the only
comparison we discuss in relation to $\ov{\CAI}$ is item deletion).

## Indices for the impact of item bias

### Impact of removing an item on $\ov{\CAI}$
$\h^{|j}(\ov{\CAI})$: Cohen's h effect size for the improvement/decrease in aggregate
CAI under PFI when the j-th item is removed:
$$\h^{|j}\ov{\CAI} = 2\arcsin\left(\sqrt{\ov{\CAI}}\right)-2\arcsin\left(\sqrt{\ov{\CAI}^{|j}}\right)$$

A negative $\h^{|j}\ov{\CAI}$ indicates an improvement (as $h^{|j}\ov{\CAI}<0 \iff \ov{\CAI}<\ov{\CAI}^{|j}$) whereas a positive $\h^{|j}\ov{\CAI}$ indicates
a deterioration in performance.

```{r include=FALSE}
# As the SFI-PFI comparisons were not as interpretable as the other indices at the moment, I temporarily removed them from the default output to make the output cleaner and more concise. 

# ### Comparing CAI under strict (SFI) vs. partial (PFI) factorial invariance
# $\h^{\sfi,\pfi}\CAI$:  Cohen's h effect sizes can be computed to quantify the discrepancy between $\CAI_{\sfi}$ vs. $\CAI$* for the full set of items. 
# \[
# \begin{align*}
# \h^{\sfi,\pfi}\CAI &= 2\text{arcsin}\left(\sqrt{\CAI^{ \sfi}}\right)-2\text{arcsin}\left(\sqrt{\CAI}\right)
# \end{align*}
# \]
# $\h^{\sfi,\pfi}\CAI^{|j}$:  Cohen's h effect size can quantifying the discrepancy between $\CAI_{\sfi}^{|j}$ vs. $\CAI^{|j}$* for the item set excluding the j-th item.
# \[
# \begin{align*}
# \h^{\sfi,\pfi}\CAI^{|j} &= 2\text{arcsin}\left(\sqrt{\CAI^{|j,\sfi}}\right)-2\text{arcsin}\left(\sqrt{\CAI^{|j}}\right)
# \end{align*}
# \]
# This index can be computed for the focal group or the reference group, e.g., $\h^{\sfi,\pfi}\CAI^{|j}_{\r}$, $\h^{\sfi,\pfi}\CAI_{\f}$ etc.

# ### Impact of removing an item on the discrepancy between $\h^{\sfi,\pfi}\CAI$ vs. $\h^{\sfi,\pfi}\CAI^{|j}$
# 
# $\Delta^{|j}\h^{\sfi,\pfi}\CAI$: Cohen's h effect size quantifying the discrepancy between $\h^{\sfi,\pfi}\CAI$ vs. $\h^{\sfi,\pfi}\CAI^{|j}$.
# In other words, the effect size of the change in bias when the j-th item is dropped.
# 
# \[
# \begin{align*}
# \Delta^{|j}\h^{\sfi,\pfi}\CAI&= \text{sign}\left(|\h^{\sfi,\pfi}\CAI| - |\h^{\sfi,\pfi}\CAI^{|j}| \right)\left||\h^{\sfi,\pfi}\CAI^{|j} |-|\h^{\sfi,\pfi}\CAI|\right|
# \end{align*}
# \]
# 
# This index can be computed for the reference group  ($\Delta^{|j}\h^{\sfi,\pfi}\CAI_{\r}$) or the focal group $\Delta^{|j}\h^{\sfi,\pfi}\CAI_{\f}$.
```

### Comparing CAI for reference (R) vs. expected focal (Ef) groups under PFI 
$\h^{\rr}\CAI$:  Cohen's h effect size quantifying the discrepancy between $\CAI_{\r}$ vs. $\ef$ for the full set of items under PFI. 
\[
\begin{align*}
\h^{\rr}\CAI &= 2\text{arcsin}\left(\sqrt{\CAI_{ \r}}\right)-2\text{arcsin}\left(\sqrt{\CAI_{\ef}}\right)
\end{align*}
\]

$\h^{\rr}\CAI^{|j}$:  Cohen's h effect size quantifying the discrepancy between $\CAI_{\r}^{|j}$ vs. $\CAI_{\ef}^{|j}$ for the item set excluding item j under PFI. 
\[
\begin{align*}
\h^{\rr}\CAI^{|j} &= 2\text{arcsin}\left(\sqrt{\CAI_{ \r}^{|j}}\right)-2\text{arcsin}\left(\sqrt{\CAI_{\ef}^{|j}}\right)
\end{align*}
\]


### Impact of removing an item on the discrepancy between  $\h^{\rr}\CAI$ vs. $\h^{\rr}\CAI^{|j}$

$\Delta^{|j}\h^{\rr}\CAI$: Cohen's h effect size quantifying the discrepancy between $\h^{\rr}\CAI$ vs. $\h^{\rr}\CAI^{|j}$.
In other words, the effect size of the change in bias when the j-th item is dropped.

\[
\begin{align*}
\Delta^{|j}\h^{\rr}\CAI&= \text{sign}\left(|\h^{\rr}\CAI| - |\h^{\rr}\CAI^{|j}| \right)\left||\h^{\rr}\CAI^{|j} |-|\h^{\rr}\CAI|\right|
\end{align*}
\]

### Illustrative Example: CES-D 
Example from Lai, Kwok, Yoon and Hsiao (2017), using the Center for Epidemiological Studies Depression (CES-D) Scale. 

We first demonstrate the use of the item deletion indices and relevant
functions by treating each subscale of the CES-D Scale as a separate factor, and assume that classification decisions will be based on the sum of the subscale scores. Then, we demonstrate the use of the item deletion indices with the full four dimensional CES-D Scale.
For all five examples, we will consider the deletion of one item at a time.

```{r}
# Zhang et al. (2011) BMC Medical Research Methodology, Tables 3-4 on page 7

# Reference group: Chinese, Focal group: Dutch

pmix_CESD_r <- 4903/(1903+4903)

# Unstandardized factor loadings
lambda_SOM_r <- lambda_SOM_f <- c(1.00, 1.03, 1.18, 1.29, 1.07, 1.02, 1.26)
lambda_DEP_r <- lambda_DEP_f <- c(1.00, 1.13, 0.82, 0.91, 1.11, 0.92, 1.06)
lambda_POS_r <- lambda_POS_f <- c(1.00, 1.66, 2.30, 2.29)
lambda_INT_r <- lambda_INT_f <- c(1.00, 0.94)

# Unstandardized intercepts
nu_SOM_r <- c(0.69, 0.56, 0.78, 0.81, 0.88, 0.74, 0.70)
nu_SOM_f <- c(0.69, 0.56, 0.78, 0.80, 0.88, 0.74, 0.70)
nu_DEP_r <- c(0.52, 0.55, 0.57, 0.42, 0.57, 0.50, 0.56)
nu_DEP_f <- c(0.52, 0.55, 0.30, 0.42, 0.57, 0.50, 0.56)
nu_POS_r <- c(1.54, 1.36, 1.16, 1.08)
nu_POS_f <- c(0.68, 1.36, 1.16, 1.08)
nu_INT_r <- nu_INT_f <- c(0.44, 0.41)

# Unstandardized uniqueness
Theta_SOM_r <- Theta_SOM_f <- diag(c(0.45, 0.37, 0.39, 0.40, 0.57, 0.51, 0.37))
Theta_DEP_r <- diag(c(0.29, 0.30, 0.41, 0.31, 0.29, 0.27, 0.24))
Theta_DEP_f <- diag(c(0.29, 0.13, 0.09, 0.14, 0.29, 0.27, 0.24))
Theta_POS_r <- diag(c(1.20, 0.81, 0.32, 0.32))
Theta_POS_f <- diag(c(0.72, 0.81, 0.32, 0.32))
Theta_INT_r <- diag(c(0.19, 0.23))
Theta_INT_f <- diag(c(0.19, 0.08))

# Latent mean differences
alpha_SOM_r <- 0
alpha_DEP_r <- 0
alpha_POS_r <- 0
alpha_INT_r <- 0
alpha_SOM_f <- -0.261
alpha_DEP_f <- -0.259
alpha_POS_f <- -0.125
alpha_INT_f <- -0.323

# Latent mean variances
psi_SOM_r <- 0.482^2
psi_SOM_f <- 0.324^2
psi_DEP_r <- 0.570^2
psi_DEP_f <- 0.318^2
psi_POS_r <- 0.354^2
psi_POS_f <- 0.329^2
psi_INT_r <- 0.574^2
psi_INT_f <- 0.184^2

# Cutoff of 16/60 on full scale. 20 items, each item scored 0-3.
```
 
### CES-D Positive Affect Factor

```{r}
#Positive Affect Factor
#Items: good (biased), hopeful, happy, enjoyed
CESD_pos <- item_deletion_h(weights_item = c(rep(1,4)), 
                              weights_latent = 1,
                              cut_z = 16/60*12,
                              #propsel = .14,  
                              alpha_r = alpha_POS_r,
                              alpha_f = alpha_POS_f,
                              psi_r = psi_POS_r,
                              psi_f = psi_POS_f,
                              lambda_r = lambda_POS_r,
                              lambda_f = lambda_POS_f,
                              nu_r = nu_POS_r,
                              nu_f = nu_POS_f,
                              Theta_r = Theta_POS_r, 
                              Theta_f = Theta_POS_f,
                              plot_contour = FALSE,
                              pmix_ref = pmix_CESD_r, 
                              print_detailed = FALSE)
CESD_pos
```

```{r include=FALSE}
# Can print out regular plots, just not the PartInv ones
#par(mar=c(4,4,.1,.1))
#plot(cars, pch=19)
```
 
```{r include=FALSE,fig.show='hold'}
print(CESD_pos$PartInv$partial$outputlist$`|1`$plot )
```
 
 The only biased item is item 1. We see from the first output table that deleting the first item increases $\ov{\SR}$ from $0.728$ to $0.756$, 
$\ov{\SE}$ from $0.728$ to $0.756$, and $\ov{\SP}$ from $0.901$ to $0.911$. The second output table shows that $h^{|1}\ov{\SR}=h^{|1}\ov{\SE}=-0.062$ and $h^{|1}\ov{\SP}=-0.035$, which suggests a slight improvement in all three $\CAI$ $(h < .20)$.

The AI ratio when the full item set is used is $0.604$, which indicates the presence of adverse impact by the four-fifths rule ($0.689<0.8$). Removing the first item achieves an AI ratio of 1, suggesting that the proportion selected for the reference group is equal to that which would have been selected for the focal group if the focal and reference groups both followed the reference group's latent score distribution (i.e., if they were matched on their true positive affect). This finding shows that removing the first item eliminates measurement bias, and is replicated in the next table comparing $\CAI_R$ with $CAI_{Ef}$ where $h^{\rr}\SR^{|1}=h^{\rr}\SE^{|1}=h^{\rr}\SP^{|1}=0$ (i.e., PS, SR, SE, and SP for the reference group are the same with the expected  PS, SR, SE, and SP for the focal group). The final table shows that the effect size of removing the first item on the difference between the reference group's CAI and the focal group's expected CAI is largest for SE and SR (small-medium effect size). 

Taken together, these improvements and the lack of any decreases in CAI suggests that the researcher may drop this item (barring any domain specific reasons not to do so).
 
### CES-D Depressive Affect Factor

```{r}
# Depressive Affect Factor 
# Items: blues, depressed, lonely, crying, sad, failure, fearful
CESD_dep <- item_deletion_h(weights_item = c(rep(1,7)), 
                             # propsel = 0.14, 
                              cut_z = 16/60*7*3,
                              n_dim = 1,  
                              alpha_r = alpha_DEP_r,
                              alpha_f = alpha_DEP_f,
                              psi_r = psi_DEP_r,
                              psi_f = psi_DEP_f,
                              lambda_r = lambda_DEP_r,
                              lambda_f = lambda_DEP_f,
                              nu_r = nu_DEP_r,
                              nu_f = nu_DEP_f,
                              Theta_r = Theta_DEP_r, 
                              Theta_f = Theta_DEP_f,
                              weights_latent = 1,
                              plot_contour = FALSE,
                              print_detailed = FALSE,
                              pmix_ref = pmix_CESD_r)
CESD_dep # items 2, 3, 4 are biased
```

 
`item_deletion_h` has determined items 2, 3, and 4 to contain some level of bias.  We see from the first table that $\ov{\SP}$ is around $0.965$ for all item deletion scenarios and $\ov{\SR}$ and $\ov{\SE}$ are slightly lower, suggesting that the depressive affect subscale is overall better at not selecting the individuals who should not be selected. We see that aggregate CAI for the full item set are higher than the other item subsets, suggesting that the removal of an item will likely not improve aggregate CAI. h values in the second table are mostly positive and indicate a slight decrease in $\ov{\CAI}$ for each item set. 

The AI ratio table shows that while removing the third item increases AI from $0.923$ to $0.994$, bias is not fully eliminated as $AI^{|3}<1$. The removal of any other items increases the discrepancy between the reference and Efocal groups. Moving on to the next two tables, we see that the removal of the third item brings $\h^{\rr}\CAI$ closer to 0, indicating an improvement that has a minimal-small effect size. Removing any other item harms CAI. 

In light of the conflicting findings and the small effect size of the potential improvement, it may be best to retain all items or choose an alternative method to item deletion for this subscale. 


### CES-D Somatic Complaints Factor

```{r}
# Somatic Complaints 
# Items: bothered, appetite, mind, effort, sleep, talk, get going
CESD_som <- item_deletion_h(weights_item = c(rep(1,7)), 
                              #propsel = .14,
                              cut_z = 16/60*7*3,
                              n_dim = 1,  
                              alpha_r = alpha_SOM_r,
                              alpha_f = alpha_SOM_f,
                              psi_r = psi_SOM_r,
                              psi_f = psi_SOM_f,
                              lambda_r = lambda_SOM_r,
                              lambda_f = lambda_SOM_f,
                              nu_r = nu_SOM_r,
                              nu_f = nu_SOM_f,
                              Theta_r = Theta_SOM_r, 
                              Theta_f = Theta_SOM_f,
                              weights_latent = 1,
                              plot_contour = FALSE,
                              print_detailed = FALSE,
                              pmix_ref = pmix_CESD_r)
CESD_som #  item 4 is biased
```
 
Removing the fourth item leads to a decrease in aggregate CAI based on the first table.
The AI ratio for the full item set is already quite high at 0.997, and increases to 1 when the fourth item is deleted. Similarly, removing this item brings the already-small difference between reference and Efocal groups on CAI to 0 with a very small effect size of around $0.003$. These findings suggest that removing the fourth item will harm CAI or lead to a negligible improvement in CAI, therefore the full item set should be retained.
 
### CES-D Interpersonal Problems Factor

```{r}
# Interpersonal Problems
# Items: unfriendly, dislike
CESD_int <- item_deletion_h(weights_item = c(rep(1,2)), 
                             # propsel = .14, 
                              cut_z = 16/60*2*3,
                              n_dim = 1,  
                              alpha_r = alpha_INT_r,
                              alpha_f = alpha_INT_f,
                              psi_r = psi_INT_r,
                              psi_f = psi_INT_f,
                              lambda_r = lambda_INT_r,
                              lambda_f = lambda_INT_f,
                              nu_r = nu_INT_r,
                              nu_f = nu_INT_f,
                              Theta_r = Theta_INT_r, 
                              Theta_f = Theta_INT_f,
                              weights_latent = 1,
                              plot_contour = TRUE,
                              print_detailed = FALSE,
                              pmix_ref = pmix_CESD_r, show_mi_result = FALSE)
CESD_int #item 2 is biased
```
 
Removing the second item in this 2-item subscale leads to lower $\ov{\CAI}$, and the effect size of this decrease is $\h \ov{\SR}=0.171$ and $\h\ov{\SE}$, which correspond to an effect size approaching $0.2$. The adverse impact ratio goes up to 1 from 0.981 and $\h^{\rr}\CAI^{|2}=0$ for all indices. The effect size of the improvement in the discrepancy between the reference and Efocal groups on SR when the second item is deleted is $\Delta^{|2}\h^{\rr}\SR=0.115$ and the other effect sizes are quite small. 

Given these conflicting findings, and the fact that this subscale only has two items, it may be best to retain both items if the subscale will be used on its own to make classification decisions.


### Full 4-Factor CES-D Scale

```{r CESD_full, include=TRUE}
lambda_CESD_r <- rbind(cbind(lambda_SOM_r, rep(0, 7), rep(0, 7), rep(0, 7)),
                       cbind(rep(0, 7), lambda_DEP_r, rep(0, 7), rep(0, 7)),
                       cbind(rep(0, 4), rep(0, 4), lambda_POS_r, rep(0, 4)),
                       cbind(rep(0, 2), rep(0, 2), rep(0, 2), lambda_INT_r))
lambda_CESD_f <- rbind(cbind(lambda_SOM_f, rep(0, 7), rep(0, 7), rep(0, 7)),
                       cbind(rep(0, 7), lambda_DEP_f, rep(0, 7), rep(0, 7)),
                       cbind(rep(0, 4), rep(0, 4), lambda_POS_f, rep(0, 4)),
                       cbind(rep(0, 2), rep(0, 2), rep(0, 2), lambda_INT_f))
psi_CESD_r <- as.matrix(c(psi_SOM_r, psi_DEP_r, psi_POS_r, psi_INT_r))
psi_CESD_f <- as.matrix(c(psi_SOM_f, psi_DEP_f, psi_POS_f, psi_INT_f))
alpha_CESD_r <- as.matrix(c(alpha_SOM_r, alpha_DEP_r, alpha_POS_r, alpha_INT_r))
alpha_CESD_f <- as.matrix(c(alpha_SOM_f, alpha_DEP_f, alpha_POS_f, alpha_INT_f))

Theta_CESD_r <- diag(c(0.45, 0.37, 0.39, 0.40, 0.57, 0.51, 0.37, #SOM
                  0.29, 0.30, 0.41, 0.31, 0.29, 0.27, 0.24, #DEP
                  1.20, 0.81, 0.32, 0.32, #POS
                  0.19, 0.23 #INT
                  ))
Theta_CESD_f <- diag(c(0.45, 0.37, 0.39, 0.40, 0.57, 0.51, 0.37, #SOM
                  0.29, 0.13, 0.09, 0.14, 0.29, 0.27, 0.24, #DEP
                  0.72, 0.81, 0.32, 0.32, #POS
                  0.23, 0.08 #INT
                  ))

nu_CESD_r <- as.matrix(c(nu_SOM_r, nu_DEP_r, nu_POS_r, nu_INT_r))
nu_CESD_f <- as.matrix(c(nu_SOM_f, nu_DEP_f, nu_POS_f, nu_INT_f))

# From Miller et al. (1997) The Factor Structure of the CES-D in Two Surveys
# of Elderly Mexican Americans p.S264; the correlation matrix of latent variables
corr_CESD <- matrix(c(1, .93, .58, .85, .93, 1, .64, .88,
                      .61, .61, 1, .55, .97, .93, .63, 1), 
                    nrow = 4, ncol = 4, byrow = TRUE)
# Compute an estimate for the variance-covariance matrix using diag(S)^-1 C diag(S) 
S <- as.matrix(sqrt(psi_CESD_f) * (1 - pmix_CESD_r) + 
                 sqrt(psi_CESD_r) * pmix_CESD_r)
psi_cesd <- diag(S) * corr_CESD * diag(S)

CESD_full <- item_deletion_h(weights_item = c(rep(1, 20)),
                            cut_z = 16,
                            n_dim = 4, n_i_per_dim = c(7, 7, 4, 2),
                            alpha_r = alpha_CESD_r,
                            alpha_f = alpha_CESD_f,
                            psi_r = psi_cesd,
                            psi_f = psi_cesd,
                            lambda_r = lambda_CESD_r,
                            lambda_f = lambda_CESD_f,
                            nu_r = nu_CESD_r,
                            nu_f = nu_CESD_f,
                            Theta_r = Theta_CESD_r,
                            Theta_f = Theta_CESD_f,
                            weights_latent = c(rep(1,4)),
                            plot_contour = FALSE,
                            print_detailed = FALSE,
                            pmix_ref = pmix_CESD_r,
                            show_mi_result = FALSE)
CESD_full
```
 
Items 4, 9, 10, 11, 15, 19, and 20 are determined to be the biased items, and correspond to SOM 4, DEP 2, DEP 3,DEP 4, POS 1, INT 1, and INT 2. Looking at the first table in the output, $\ov{\CAI}$ decrease in all item deletion scenarios, 
with the exception of $\ov{\SR}^{|10}$ going up by 0.001 points which is unlikely 
to be a significant improvement. The second table shows negative h values for 
$\ov{\SR}^{|10}$ and $\ov{\SP}^{|10}$, in agreement of the very small improvement
achieved if the 10-th item (DEP 3)  is dropped. We see the largest increase in AI
ratio if item 15 (POS 1) is dropped: $AI=0.744$ to $AI^{|15}=0.924$, indicating
thatthis item is a strong candidate for deletion. The second largest increase is 
achieved by the deletion of item 10, with $AI^{10}=0.802$. The comparison of 
CAI for the reference group with the expected CAI for the focal group in the next
table shows that the discrepancy between $\CAI_r$ and $\CAI_{Ef}$ is smallest if item 15 is deleted as $\h^{\rr}\PS=0.131$ goes down to $\h^{\rr}\PS^{|15}=0.037$, $\h^{\rr}\SR=-0.234$ goes up to $\h^{\rr}\SR^{|15}=-0.073$, $\h^{\rr}\SE=0.227$ goes down to $\h^{\rr}\SE^{|15}=0.047$ and $\h^{\rr}\SP=-0.158$ goes up to $\h^{\rr}\SP^{|15}=-0.050$. Note that we judge improvement by the magnitude of the
difference rather than the direction. In the comparison between CAI for reference vs. Efocal groups, the direction of the difference indicates the group that is benefiting from the bias. We would like to minimize bias regardless of group membership, but the signs of the indices nevertheless give valuable information 
about the classification process. The 10-th item is the only other item that appears
to lead to some reduction in the discrepancy between $\CAI_r$ and $\CAI_{Ef}$. 
Moving on to the final table, we see that removing the 15-th item would have the
largest impact on the discrepancy between $\CAI_r$ and $\CAI_{Ef}$, followed by
the deletion of the 10-th item.

Overall, the researcher may consider deleting either the 15-th or the 10-th item 
using their domain specific expertise and consulting existing literature to choose 
between the two items. The output object from item_deletion_h contains other tables
that may aid the researcher in this process. For instance, the outputs of PartInv()
may be examined for the two item deletion scenarios:

All items retained:

```{r}
CESD_full$PartInv$partial$outputlist$full
```

Subset excluding item 15:

```{r}
CESD_full$PartInv$partial$outputlist$`|15`
```

```{r include=FALSE, echo=FALSE}
# plot not embedded in knitted vignette, need to fix
CESD_full$PartInv$partial$outputlist$`|15`
CESD_full$PartInv$partial$outputlist$`|15`$plot
```


```{r include=FALSE, echo=FALSE}
AA <- PartInv(weights_item = c(rep(1,7)), 
                              propsel = .14,
                              alpha_r = alpha_DEP_r,
                              alpha_f = alpha_DEP_f,
                              psi_r = psi_DEP_r,
                              psi_f = psi_DEP_f,
                              lambda_r = lambda_DEP_r,
                              lambda_f = lambda_DEP_f,
                              nu_r = nu_DEP_r,
                              nu_f = nu_DEP_f,
                              Theta_r = Theta_DEP_r, 
                              Theta_f = Theta_DEP_f,
                              weights_latent = 1,
                              plot_contour = TRUE,
                              pmix_ref = pmix_CESD_r, labels=c("Chinese", "Dutch"))
AA
a<- item_deletion_h(weights_item = c(rep(1,7)), 
                              propsel = .14, 
                              alpha_r = alpha_DEP_r,
                              alpha_f = alpha_DEP_f,
                              psi_r = psi_DEP_r,
                              psi_f = psi_DEP_f,
                              lambda_r = lambda_DEP_r,
                              lambda_f = lambda_DEP_f,
                              nu_r = nu_DEP_r,
                              nu_f = nu_DEP_f,
                              Theta_r = Theta_DEP_r, 
                              Theta_f = Theta_DEP_f,
                              weights_latent = 1,
                              plot_contour = FALSE,
                              pmix_ref = pmix_CESD_r, 
                              labels=c("Chinese", "Dutch"),
                              n_dim = 1, print_detailed=FALSE)
a
```

```{r}
# run item_deletion_h() after dropping item 15 (POS1)
CESD_full_drop15 <- item_deletion_h(weights_item = c(rep(1,14), 0, 
                                                     rep(1.33333, 3), 1, 1),
                            cut_z = 16,
                            n_dim = 4, n_i_per_dim = c(7, 7, 4, 2),
                            alpha_r = alpha_CESD_r,
                            alpha_f = alpha_CESD_f,
                            psi_r = psi_cesd,
                            psi_f = psi_cesd,
                            lambda_r = lambda_CESD_r,
                            lambda_f = lambda_CESD_f,
                            nu_r = nu_CESD_r,
                            nu_f = nu_CESD_f,
                            Theta_r = Theta_CESD_r,
                            Theta_f = Theta_CESD_f,
                            weights_latent = c(rep(1,4)),
                            plot_contour = TRUE,
                            print_detailed = FALSE,
                            pmix_ref = pmix_CESD_r,
                            show_mi_result = FALSE)
CESD_full_drop15
```

All items retained:

```{r}
CESD_full_drop15$PartInv$partial$outputlist$full
```

Subset excluding item 10:

```{r}
CESD_full_drop15$PartInv$partial$outputlist$`|10`
```

Now to illustrate `print_detailed=TRUE`:

```{r}
CESD_pos <- item_deletion_h(weights_item = c(rep(1,4)), 
                              weights_latent = 1,
                              cut_z = 16/60*12,
                              #propsel = .14,  
                              alpha_r = alpha_POS_r,
                              alpha_f = alpha_POS_f,
                              psi_r = psi_POS_r,
                              psi_f = psi_POS_f,
                              lambda_r = lambda_POS_r,
                              lambda_f = lambda_POS_f,
                              nu_r = nu_POS_r,
                              nu_f = nu_POS_f,
                              Theta_r = Theta_POS_r, 
                              Theta_f = Theta_POS_f,
                              plot_contour = FALSE,
                            show_mi_result = FALSE,
                              pmix_ref = pmix_CESD_r, 
                              print_detailed = FALSE)
CESD_pos
CESD_pos$PartInv$partial$outputlist$`|1`$plot
```

Now to illustrate the use of `user_specified_items`:

```{r }
CESD_pos <- item_deletion_h(weights_item = c(rep(1,4)), 
                              weights_latent = 1,
                              cut_z = 16/60*12,
                              #propsel = .14,  
                              alpha_r = alpha_POS_r,
                              alpha_f = alpha_POS_f,
                              psi_r = psi_POS_r,
                              psi_f = psi_POS_f,
                              lambda_r = lambda_POS_r,
                              lambda_f = lambda_POS_f,
                              nu_r = nu_POS_r,
                              nu_f = nu_POS_f,
                              Theta_r = Theta_POS_r, 
                              Theta_f = Theta_POS_f,
                              plot_contour = FALSE,
                              pmix_ref = pmix_CESD_r, 
                              print_detailed = TRUE,
                              user_specified_items = c(1:3)
                            )
CESD_pos
```