---
title: "Applied examples"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Applied examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE, warning=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, warning=FALSE, message=FALSE}
library(PartInvShinyUI)
library(lavaan)
```
\newcommand{\SR}{\text{SR}}
\newcommand{\CAI}{\text{CAI}}
\newcommand{\SE}{\text{SE}}
\newcommand{\SP}{\text{SP}}
\newcommand{\PS}{\text{PS}}
\newcommand{\TP}{\text{TP}}
\newcommand{\FN}{\text{FN}}
\newcommand{\FP}{\text{FP}}
\newcommand{\TN}{\text{TN}}
\newcommand{\sfi}{\text{sfi}}
\newcommand{\pfi}{\text{pfi}}
\newcommand{\ef}{\text{Ef}}
\newcommand{\r}{\text{r}}
\newcommand{\f}{\text{f}}
\newcommand{\rr}{\text{r-Ef}}
\newcommand{\h}{\text{h}}
\newcommand{\ov}{\overline}

## Classification Accuracy Indices: Formulas and Notation

### Classification Accuracy Index (CAI)

- Proportion Selected: $\PS=\text{P(TP)}+\text{P(FP)}$

- Success Ratio: $\SP=\dfrac{\text{P(TP)}}{\text{P(TP)}+\text{P(FP)}}$

- Sensitivity: $\SE=\dfrac{\text{P(TP)}}{\text{P(TP)}+\text{P(FN)}}$

- Specificity: $\SP=\dfrac{\text{P(TN)}}{\text{P(TN)}+\text{P(FP)}}$

Unless otherwise indicated, we will assume that the full item set (length J) is
used and that partial factorial invariance (PFI) holds. 

If strict factorial invariance (SFI) holds, this will be denoted as $\CAI_{\sfi}$, e.g., $\SE_{\sfi}$ for SE under SFI.

A CAI computed on an item set excluding item $j \in \{1,\ldots,J\}$ is denoted $\CAI^{|j}$, e.g., $\SE^{|2}$ if SE is computed on the item set excluding the second item.  

### Composite Classification Accuracy Index $\left(\ov{\CAI}\right)$

- Composite PS: $\ov{\PS}  = \TP_{r}\times p_r + \TP_{f}\times (1-p_r) + \FP_{r}\times p_r + \FP_{f}\times (1-p_r)$

- Composite SR: $\ov{\SR} = \dfrac{\TP_{r}\times p_r + \TP_{f}\times (1-p_r)}{\TP_{r}\times p_r + \TP_{f}\times (1-p_r) + \FP_{r}\times p_r + \FP_{f}\times (1-p_r)}$
 
- Composite SE: $\ov{\SE} = \dfrac{\TP_{r}\times p_r + \TP_{f}\times (1-p_r)}{\TP_{r}\times p_r + \TP_{f}\times (1-p_r) + \FN_{r}\times p_r + \FN_{f}\times (1-p_r)}$

- Composite SP: $\ov{\SP} = \dfrac{\TN_{r}\times p_r + \TN_{f}\times (1-p_r)}{\TN_{r}\times p_r + \TN_{f}\times (1-p_r) + \FP_{r}\times p_r + \FP_{f}\times (1-p_r)}$

$\ov{\CAI}$ is only computed for the partial invariance case (hence, the only
comparison we discuss in relation to $\ov{\CAI}$ is item deletion).

## Indices for the impact of item bias

### Impact of removing an item on $\ov{\CAI}$
$\h^{|j}(\ov{\CAI})$: Cohen's h effect size for the improvement/decrease in overall
CAI under PFI when the j-th item is removed:
$$\h^{|j}\ov{\CAI} = 2\arcsin\left(\sqrt{\ov{\CAI}}\right)-2\arcsin\left(\sqrt{\ov{\CAI}^{|j}}\right)$$

A negative $\h^{|j}\ov{\CAI}$ indicates an improvement (as $h^{|j}\ov{\CAI}<0 \iff \ov{\CAI}<\ov{\CAI}^{|j}$) whereas a positive $\h^{|j}\ov{\CAI}$ indicates
a deterioration in performance.

### Comparing CAI under strict (SFI) vs. partial (PFI) factorial invariance
$\h^{\sfi,\pfi}\CAI$:  Cohen's h effect sizes can be computed to quantify the discrepancy between $\CAI_{\sfi}$ vs. $\CAI$* for the full set of items. 
\[
\begin{align*}
\h^{\sfi,\pfi}\CAI &= 2\text{arcsin}\left(\sqrt{\CAI^{ \sfi}}\right)-2\text{arcsin}\left(\sqrt{\CAI}\right)
\end{align*}
\]
$\h^{\sfi,\pfi}\CAI^{|j}$:  Cohen's h effect size can quantifying the discrepancy between $\CAI_{\sfi}^{|j}$ vs. $\CAI^{|j}$* for the item set excluding the j-th item.
\[
\begin{align*}
\h^{\sfi,\pfi}\CAI^{|j} &= 2\text{arcsin}\left(\sqrt{\CAI^{|j,\sfi}}\right)-2\text{arcsin}\left(\sqrt{\CAI^{|j}}\right)
\end{align*}
\]
* note that $_\pfi$ is omitted as we are assuming the default is PFI.

This index can be computed for the focal group or the reference group, e.g., $\h^{\sfi,\pfi}\CAI^{|j}_{\r}$, $\h^{\sfi,\pfi}\CAI_{\f}$ etc.

### Comparing CAI for reference (R) vs. expected focal (Ef) groups under PFI 
$\h^{\rr}\CAI$:  Cohen's h effect size quantifying the discrepancy between $\CAI_{\r}$ vs. $\ef$ for the full set of items under PFI. 
\[
\begin{align*}
\h^{\rr}\CAI &= 2\text{arcsin}\left(\sqrt{\CAI_{ \r}}\right)-2\text{arcsin}\left(\sqrt{\CAI_{\ef}}\right)
\end{align*}
\]

$\h^{\rr}\CAI^{|j}$:  Cohen's h effect size quantifying the discrepancy between $\CAI_{\r}^{|j}$ vs. $\CAI_{\ef}^{|j}$ for the item set excluding item j under PFI. 
\[
\begin{align*}
\h^{\rr}\CAI^{|j} &= 2\text{arcsin}\left(\sqrt{\CAI_{ \r}^{|j}}\right)-2\text{arcsin}\left(\sqrt{\CAI_{\ef}^{|j}}\right)
\end{align*}
\]

### Impact of removing an item on the discrepancy between $\h^{\sfi,\pfi}\CAI$ vs. $\h^{\sfi,\pfi}\CAI^{|j}$

$\Delta^{|j}\h^{\sfi,\pfi}\CAI$: Cohen's h effect size quantifying the discrepancy between $\h^{\sfi,\pfi}\CAI$ vs. $\h^{\sfi,\pfi}\CAI^{|j}$.
In other words, the effect size of the change in bias when the j-th item is dropped.

\[
\begin{align*}
\Delta^{|j}\h^{\sfi,\pfi}\CAI&= \text{sign}\left(|\h^{\sfi,\pfi}\CAI| - |\h^{\sfi,\pfi}\CAI^{|j}| \right)\left||\h^{\sfi,\pfi}\CAI^{|j} |-|\h^{\sfi,\pfi}\CAI|\right|
\end{align*}
\]

This index can be computed for the reference group  ($\Delta^{|j}\h^{\sfi,\pfi}\CAI_{\r}$) or the focal group $\Delta^{|j}\h^{\sfi,\pfi}\CAI_{\f}$.

### Impact of removing an item on the discrepancy between  $\h^{\rr}\CAI$ vs. $\h^{\rr}\CAI^{|j}$

$\Delta^{|j}\h^{\rr}\CAI$: Cohen's h effect size quantifying the discrepancy between $\h^{\rr}\CAI$ vs. $\h^{\rr}\CAI^{|j}$.
In other words, the effect size of the change in bias when the j-th item is dropped.

\[
\begin{align*}
\Delta^{|j}\h^{\rr}\CAI&= \text{sign}\left(|\h^{\rr}\CAI| - |\h^{\rr}\CAI^{|j}| \right)\left||\h^{\rr}\CAI^{|j} |-|\h^{\rr}\CAI|\right|
\end{align*}
\]

## Example 1: CES-D 
Example from Lai, Kwok, Yoon and Hsiao (2017) 
Center for Epidemiological Studies Depression  (CES-D) Scale 

```{r}
# Zhang et al. (2011) BMC Medical Research Methodology, Tables 3-4 on page 7

# Reference group: Chinese, Focal group: Dutch
# 5:2 ratio, mixing proportion of 5/7

pmix_CESD_r <- 5/7

# Unstandardized factor loadings
lambda_SOM_r <- lambda_SOM_f <- c(1.00, 1.03, 1.18, 1.29, 1.07, 1.02, 1.26)
lambda_DEP_r <- lambda_DEP_f <- c(1.00, 1.13, 0.82, 0.91, 1.11, 0.92, 1.06)
lambda_POS_r <- lambda_POS_f <- c(1.00, 1.66, 2.30, 2.29)
lambda_INT_r <- lambda_INT_f <- c(1.00, 0.94)

# Unstandardized intercepts
nu_SOM_r <- c(0.69, 0.56, 0.78, 0.81, 0.88, 0.74, 0.70)
nu_SOM_f <- c(0.69, 0.56, 0.78, 0.80, 0.88, 0.74, 0.70)
nu_DEP_r <- c(0.52, 0.55, 0.57, 0.42, 0.57, 0.50, 0.56)
nu_DEP_f <- c(0.52, 0.55, 0.30, 0.42, 0.57, 0.50, 0.56)
nu_POS_r <- c(1.54, 1.36, 1.16, 1.08)
nu_POS_f <- c(0.68, 1.36, 1.16, 1.08)
nu_INT_r <- nu_INT_f <- c(0.44, 0.41)

# Unstandardized uniqueness
Theta_SOM_r <- Theta_SOM_f <- diag(c(0.45, 0.37, 0.39, 0.40, 0.57, 0.51, 0.37))
Theta_DEP_r <- diag(c(0.29, 0.30, 0.41, 0.31, 0.29, 0.27, 0.24))
Theta_DEP_f <- diag(c(0.29, 0.13, 0.09, 0.14, 0.29, 0.27, 0.24))
Theta_POS_r <- diag(c(1.20, 0.81, 0.32, 0.32))
Theta_POS_f <- diag(c(0.72, 0.81, 0.32, 0.32))
Theta_INT_r <- diag(c(0.19, 0.23))
Theta_INT_f <- diag(c(0.19, 0.08))

# Latent mean differences
alpha_SOM_r <- 0
alpha_DEP_r <- 0
alpha_POS_r <- 0
alpha_INT_r <- 0
alpha_SOM_f <- -0.261
alpha_DEP_f <- -0.259
alpha_POS_f <- -0.125
alpha_INT_f <- -0.323

# Latent mean variances
psi_SOM_r <- 0.482^2
psi_SOM_f <- 0.324^2
psi_DEP_r <- 0.570^2
psi_DEP_f <- 0.318^2
psi_POS_r <- 0.354^2
psi_POS_f <- 0.329^2
psi_INT_r <- 0.574^2
psi_INT_f <- 0.184^2
```
 
```{r CESD_full, include=FALSE}
lambda_CESD_r <- rbind(cbind(lambda_SOM_r, rep(0, 7), rep(0, 7), rep(0, 7)),
                       cbind(rep(0, 7), lambda_DEP_r, rep(0, 7), rep(0, 7)),
                       cbind(rep(0, 4), rep(0, 4), lambda_POS_r, rep(0, 4)),
                       cbind(rep(0, 2), rep(0, 2), rep(0, 2), lambda_INT_r))
lambda_CESD_f <- rbind(cbind(lambda_SOM_f, rep(0, 7), rep(0, 7), rep(0, 7)),
                       cbind(rep(0, 7), lambda_DEP_f, rep(0, 7), rep(0, 7)),
                       cbind(rep(0, 4), rep(0, 4), lambda_POS_f, rep(0, 4)),
                       cbind(rep(0, 2), rep(0, 2), rep(0, 2), lambda_INT_f))
psi_CESD_r <- as.matrix(c(psi_SOM_r, psi_DEP_r, psi_POS_r, psi_INT_r))
psi_CESD_f <- as.matrix(c(psi_SOM_f, psi_DEP_f, psi_POS_f, psi_INT_f))
alpha_CESD_r <- as.matrix(c(alpha_SOM_r, alpha_DEP_r, alpha_POS_r, alpha_INT_r))
alpha_CESD_f <- as.matrix(c(alpha_SOM_f, alpha_DEP_f, alpha_POS_f, alpha_INT_f))

Theta_CESD_r <- diag(c(0.45, 0.37, 0.39, 0.40, 0.57, 0.51, 0.37, #SOM
                  0.29, 0.30, 0.41, 0.31, 0.29, 0.27, 0.24, #DEP
                  1.20, 0.81, 0.32, 0.32, #POS
                  0.19, 0.23 #INT
                  ))
Theta_CESD_f <- diag(c(0.45, 0.37, 0.39, 0.40, 0.57, 0.51, 0.37, #SOM
                  0.29, 0.13, 0.09, 0.14, 0.29, 0.27, 0.24, #DEP
                  0.72, 0.81, 0.32, 0.32, #POS
                  0.23, 0.08 #INT
                  ))

nu_CESD_r <- as.matrix(c(nu_SOM_r, nu_DEP_r, nu_POS_r, nu_INT_r))
nu_CESD_f <- as.matrix(c(nu_SOM_f, nu_DEP_f, nu_POS_f, nu_INT_f))

# From Miller et al. (1997) The Factor Structure of the CES-D in Two Surveys
# of Elderly Mexican Americans p.S264; the correlation matrix of latent variables
corr_CESD <- matrix(c(1, .93, -.58, .85, .93, 1, -.64, .88,
                      -.61, -.61, 1, -.55, .97, .93, -.63, 1), 
                    nrow = 4, ncol = 4, byrow = TRUE)
# Compute an estimate for the variance-covariance matrix using diag(S)^-1 C diag(S) 
S <- as.matrix(sqrt(psi_CESD_f) * (1 - pmix_CESD_r) + 
                 sqrt(psi_CESD_r) * pmix_CESD_r)
psi_cesd <- diag(S) * corr_CESD * diag(S)

CESD_full <- item_deletion_h(weights_item = c(rep(1, 20)),
                            propsel = .14, 
                            n_dim = 4, n_i_per_dim = c(7, 7, 4, 2),
                            alpha_r = alpha_CESD_r,
                            alpha_f = alpha_CESD_f,
                            psi_r = psi_cesd,
                            psi_f = psi_cesd,
                            lambda_r = lambda_CESD_r,
                            lambda_f = lambda_CESD_f,
                            nu_r = nu_CESD_r,
                            nu_f = nu_CESD_f,
                            Theta_r = Theta_CESD_r,
                            Theta_f = Theta_CESD_f,
                            weights_latent = c(rep(1,4)),
                            plot_contour = FALSE,
                            return_detailed = FALSE,
                            pmix_ref = pmix_CESD_r)
CESD_full # items 4, 9, 10, 11, 15, 19, 20
# These items correspond to SOM 4, DEP 2, 3, 4, POS 1, INT 1, 2
```
 
 
```{r}
#Positive Affect Factor
#Items: good (biased), hopeful, happy, enjoyed
CESD_pos <- item_deletion_h(weights_item = c(rep(1,4)), 
                              propsel = .14, n_dim = 1,  
                              alpha_r = alpha_POS_r,
                              alpha_f = alpha_POS_f,
                              psi_r = psi_POS_r,
                              psi_f = psi_POS_f,
                              lambda_r = lambda_POS_r,
                              lambda_f = lambda_POS_f,
                              nu_r = nu_POS_r,
                              nu_f = nu_POS_f,
                              Theta_r = Theta_POS_r, 
                              Theta_f = Theta_POS_f,
                              weights_latent = 1,
                              plot_contour = FALSE,
                              return_detailed = FALSE,
                              pmix_ref = pmix_CESD_r, 
                           # biased_items_only=TRUE 
                           )
CESD_pos 

# Depressive Affect Factor 
# Items: blues, depressed, lonely, crying, sad, failure, fearful
CESD_dep <- item_deletion_h(weights_item = c(rep(1,7)), 
                              propsel = .14, n_dim = 1,  
                              alpha_r = alpha_DEP_r,
                              alpha_f = alpha_DEP_f,
                              psi_r = psi_DEP_r,
                              psi_f = psi_DEP_f,
                              lambda_r = lambda_DEP_r,
                              lambda_f = lambda_DEP_f,
                              nu_r = nu_DEP_r,
                              nu_f = nu_DEP_f,
                              Theta_r = Theta_DEP_r, 
                              Theta_f = Theta_DEP_f,
                              weights_latent = 1,
                              plot_contour = FALSE,
                              return_detailed = FALSE,
                              pmix_ref = pmix_CESD_r, 
                            biased_items_only = TRUE)
CESD_dep # items 2, 3, 4 are biased

# Somatic Complaints 
# Items: bothered, appetite, mind, effort, sleep, talk, get going
CESD_som <- item_deletion_h(weights_item = c(rep(1,7)), 
                              propsel = .14, n_dim = 1,  
                              alpha_r = alpha_SOM_r,
                              alpha_f = alpha_SOM_f,
                              psi_r = psi_SOM_r,
                              psi_f = psi_SOM_f,
                              lambda_r = lambda_SOM_r,
                              lambda_f = lambda_SOM_f,
                              nu_r = nu_SOM_r,
                              nu_f = nu_SOM_f,
                              Theta_r = Theta_SOM_r, 
                              Theta_f = Theta_SOM_f,
                              weights_latent = 1,
                              plot_contour = FALSE,
                              return_detailed = TRUE,
                              pmix_ref = pmix_CESD_r)
CESD_som #  item 4 is biased (?)

# Interpersonal Problems
# Items: unfriendly, dislike
CESD_int <- item_deletion_h(weights_item = c(rep(1,2)), 
                              propsel = .14, n_dim = 1,  
                              alpha_r = alpha_INT_r,
                              alpha_f = alpha_INT_f,
                              psi_r = psi_INT_r,
                              psi_f = psi_INT_f,
                              lambda_r = lambda_INT_r,
                              lambda_f = lambda_INT_f,
                              nu_r = nu_INT_r,
                              nu_f = nu_INT_f,
                              Theta_r = Theta_INT_r, 
                              Theta_f = Theta_INT_f,
                              weights_latent = 1,
                              plot_contour = FALSE,
                              return_detailed = TRUE,
                              pmix_ref = pmix_CESD_r)
CESD_int #item 2 is biased
```




For the 4-item CES-D scale, the negative $h^{|1}(\ov{\SR})$,
$h^{|1}(\ov{\SE})$, and $h^{|1}(\ov{\SP})$ values 
indicate that removing the first item would lead to an improvement in SR, 
SE, and SP. On the other hand, the positive $h$ values for modified item sets 
excluding items 2, 3, or 4 suggest that SR, SE, and SP decreases if any of these 
items are dropped.




#### `delta_h$h_R_vs_Ef.par`

HL: # (I would suggest separating out PS from SR, SE, and SP here, as PS is more a fairness index whereas SR, SE, SP are more about accuracy. We may only need delta h for PS. )


Looking at PS, Delta h is only positive for the comparison between the full item
set and the set where item 1 is deleted. As we know that item 1 is biased, this 
indicates that seeing a positive delta h in PS is an indication that that item
should be removed. We see the opposite patterns for item 1 vs. items 2-4 where 
removing any of item 2, 3, or 4 would harm the accuracy indices.



#### `h$R_vs_Ef.par`
[HL]: # (We can call the following 'bias'. It'd be helpful to discuss the 'full' column first.)



$\PS^{|1}_{\rr}=0$,$\SR^{|1}_{\rr}=0$,
$\SE^{|1}_{\rr=0}$, $\SP^{|1}_{\rr}=0$ suggest that 
if we delete the first item, the accuracy indices for the Efocal group under
PFI will be equal to that of the reference group under PFI, *thus removing bias*. 

$\PS_{\rr}=0.203$ indicates the proportion selected in the reference group is
larger than the proportion selected in Efocal. In other words, *the reference group is favored when the full set of items are used*. Under the expected distribution for the 
reference group, the focal group would have a higher success ratio and a higher
specificity than the reference group when for item sets $\{I, I^{|2}, I^{|3}, I^{|4}\}$ but would have a lower proportion selected and a lower sensitivity.
Dropping any item other than the first item would lead to a similar situation where
a greater proportion is selected from the reference group than the focal group
and is not advisable despite leading to an increase in SE.


$\PS^{r}_{\sfi,\pfi}=-0.040$ indicates that 
PS was slightly higher under PFI compared to under SFI for the full item set and when any of items 2-4 was deleted. Deleting
item 1 brought the effect size of the difference between SFI and PFI conditions to 0 for all accuracy indices.

## Example 2:  Millsap, Kwok (2004)
'Evaluating the Impact of Partial Factorial Invariance on
Selection in Two Populations'

Biased items: 3, 4
```{r}
# Worry subscale of the test anxiety inventory
ex2 <- item_deletion_h(weights_item = c(1, 1, 1, 1, 1, 1, 1, 1), 
                              propsel = 0.1000001,#"90% cutpoint"
                              #cut_z= 23.29952,
                             n_dim = 1,  
                             alpha_r = 0,
                             alpha_f =-0.126,
                             psi_r = 0.544,
                             psi_f = 0.477,
                             lambda_r = c(0.836, 1, 0.904, 0.808, 0.903,
                                             0.960, 0.934, 0.934),
                             lambda_f = c(0.836, 1, 1.111, 1.001, 0.903, 
                                             0.960, 0.934, 0.934),
                             nu_r = c(2.114, 2.064, 1.901, 2.004, 2.144,
                                        1.985, 2.179, 2.230),
                             nu_f= c(2.114, 2.064, 1.880, 1.985, 2.144,
                                        1.985, 2.179, 2.230),
                             Theta_r = diag(c(.517, .523, .631, .585, .481,
                                                .469,.551,.572)),
                             Theta_f = diag(c(.514, .407, .371, .475, .392,
                                                .335,.454,.457)),
                             weights_latent = 1,
                             plot_contour = FALSE,
                             return_detailed = FALSE, pmix_ref = 0.5)
```



```{r}
ex2
```

The positive h values in h_overall_CAI_par suggest that no item should be 
dropped, as dropping any of the items would lead to a lower success ratio, lower
sensitivity, and lower specificity.

`h$R_vs_Ef.par`

If the focal group followed the same distribution as the reference group, a larger
proportion would be selected for the focal group compared to the reference group 
(indicated by the negative PS) when all items are used. If any one item is dropped
there would be an increase in PS for the reference group, leading to a positive h.




A greater proportion is selected under SFI compared to PFI when all items are used, but when any of the 8 items are dropped, a 
greater proportion is selected under PFI. SR, SE, SP are always
positive, indicating that regardless of item drop condition, 
SR, SE, SP under SFI is always larger than SR, SE, SP under PFI. 



## Example 3: Mini-IPIP - Ock, McAbee, Mulfinger, and Oswald (2020)
'The Practical Effects of Measurement Invariance: Gender Invariance in Two Big Five Personality Measures'
Biased items: 1, 7, 11, 13, 14
```{r read data, include  = FALSE}
data <- read.table("IPIPFFM.dat", header = TRUE)
head(data)
male <- data[data$sex == 1, ]
female <- data[data$sex == 2, ]
```

```{r specify and fit model}
model <- 'A =~  a2 + a5  + a7 + a9
          C =~  c3 + c4 + c8 + c9
          E =~ e1 + e4 + e6 + e7
          N =~ n1 + n2 + n6 + n8
          O =~ i2 + i8 + i9 + i10
          a2 ~~ a5
          e4 ~~ e7  
          i2 ~~ i10
          i8 ~~ i9
          a9 ~~ i9
          c3 ~~ e6
          a2 ~~ e7
          e7 ~~ n2'
fit_strict <- cfa(model, data = data, group = "sex",
                  group.equal = c("loadings", "Intercepts", "residuals"),
                  group.partial = c("e6 ~ 1", "n1 ~ 1", "n2 ~ 1", "a2 ~ 1", 
                                    #items  1 (A2), 7 (C8), 11 (E6), 13 (N1), 14 (N2)
                                    "n2 ~~ n2", "n1 ~~ n1", "c8 ~~ c8"),
                  estimator = "MLR", std.lv = TRUE)
result <- lavInspect(fit_strict, what = "est")
```

```{r IPIPFFM item deletion}
ex3 <- item_deletion_h(propsel=0.25,
              weights_item = c(3.1385, 3.1385, 3.1385, 3.1385,
                                8.3203, 8.3203, 8.3203, 8.3203,
                                5.1586, 5.1586, 5.1586, 5.1586,
                                -6.5870, -6.5870, -6.5870, -6.5870,
                                1.7957, 1.7957, 1.7957, 1.7957), 
              n_dim = 5, 
              alpha_r = result[[2]]$alpha,
              alpha_f = result[[1]]$alpha,
              psi_r = result[[2]]$psi,
              psi_f = result[[1]]$psi,
              lambda_r = result[[2]]$lambda,
              lambda_f = result[[1]]$lambda,
              nu_r = result[[2]]$nu,
              nu_f = result[[1]]$nu,
              Theta_r = result[[2]]$theta,
              Theta_f = result[[1]]$theta,
              weights_latent = c(0.12553907, 0.33281060, 0.20634298, 
                                 -0.26347936, 0.07182799),
              plot_contour = FALSE, 
              return_detailed = FALSE,
              user_specified_items = c(1,7,11,13,14))
```

```{r}
ex3
```

Looking at `h_overall_par`, we see that dropping item 1 would lead to
a marginal improvement in SR and SP, while SE would be unaffected. We see a similar
pattern with item 18. 

Item 12 appears to be a bad item to drop as dropping this item produces the highest
h values (i.e., the largest decrease in SR, SE, and SP) in this example, followed
by items 10 and 11. Conversely, removing item 4 would not harm SR, SP, or SE.

Out of the biased items (1, 7, 11, 13, and 14), we should consider dropping item 1
and retaining item 11.

When item 11 is dropped, h for PS is negative (a higher proportion is selected 
under Efocal than the reference group). For all other item drop conditions, h for 
PS is positive. 