---
title: "Applied examples of item deletion statistics"
output: 
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Applied examples of item deletion statistics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE, warning=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

\newcommand{\SR}{\text{SR}}
\newcommand{\CAI}{\text{CAI}}
\newcommand{\SE}{\text{SE}}
\newcommand{\SP}{\text{SP}}
\newcommand{\PS}{\text{PS}}
\newcommand{\TP}{\text{TP}}
\newcommand{\FN}{\text{FN}}
\newcommand{\FP}{\text{FP}}
\newcommand{\TN}{\text{TN}}
\newcommand{\sfi}{\text{sfi}}
\newcommand{\pfi}{\text{pfi}}
\newcommand{\ef}{\text{Ef}}
\newcommand{\r}{\text{r}}
\newcommand{\f}{\text{f}}
\newcommand{\rr}{\text{r-Ef}}
\newcommand{\ov}{\overline}

## Formulas and Notation

### Classification Accuracy Indices (CAI)

- Proportion Selected: $\PS=\text{P(TP)}+\text{P(FP)}$

- Success Ratio: $\SR=\dfrac{\text{P(TP)}}{\text{P(TP)}+\text{P(FP)}}$

- Sensitivity: $\SE=\dfrac{\text{P(TP)}}{\text{P(TP)}+\text{P(FN)}}$

- Specificity: $\SP=\dfrac{\text{P(TN)}}{\text{P(TN)}+\text{P(FP)}}$

Unless otherwise indicated, we will assume that the full item set (length J) is
used and that partial factorial invariance (PFI) holds. 

If strict factorial invariance (SFI) holds, this will be denoted as $\CAI_{\sfi}$, e.g., $\SE_{\sfi}$ for SE under SFI.

A CAI computed on an item set excluding item $j \in \{1,\ldots,J\}$ is denoted $\CAI^{|j}$, e.g., $\SE^{|2}$ if SE is computed on the item set excluding the second item.  

### Aggregate Classification Accuracy Indices $\left(\ov{\CAI}\right)$

Given $p_f = 1 - p_r$,

- Aggregate SR: 
$$\ov{\SR} = \dfrac{\TP_{r}\times p_r + \TP_{f}\times p_f}{\TP_{r}\times p_r + \TP_{f}\times p_f + \FP_{r}\times p_r + \FP_{f}\times p_f}$$
 
- Aggregate SE: 
$$\ov{\SE} = \dfrac{\TP_{r}\times p_r + \TP_{f}\times p_f}{\TP_{r}\times p_r + \TP_{f}\times p_f + \FN_{r}\times p_r + \FN_{f}\times p_f}$$

- Aggregate SP: 
$$\ov{\SP} = \dfrac{\TN_{r}\times p_r + \TN_{f}\times p_f}{\TN_{r}\times p_r + \TN_{f}\times p_f + \FP_{r}\times p_r + \FP_{f}\times p_f}$$

$\ov{\CAI}$ is only computed for the partial invariance case (hence, the only
comparison we discuss in relation to $\ov{\CAI}$ is item deletion).

## Indices for the impact of item bias

### Impact of removing an item on $\ov{\CAI}$
$h^{|j}\ov{\CAI}$: Cohen's $h$ effect size for the improvement/decrease in aggregate
CAI under PFI when the $j$-th item is removed:
$$h^{|j}\ov{\CAI} = 2\arcsin\left(\sqrt{\ov{\CAI}}\right)-2\arcsin\left(\sqrt{\ov{\CAI}^{|j}}\right)$$

A negative $h^{|j}\ov{\CAI}$ indicates an improvement (as $h^{|j}\ov{\CAI}<0 \iff \ov{\CAI}<\ov{\CAI}^{|j}$) whereas a positive $h^{|j}\ov{\CAI}$ indicates
a deterioration in performance.

### Comparing CAI for reference (R) vs. expected focal (Ef) groups 
$h^{\rr}\CAI$: Cohen's $h$ effect size quantifying the discrepancy between $\CAI_{\r}$ vs. $\ef$ for the full set of items under PFI. 
\[
\begin{align*}
 h^{\rr}\CAI &= 2\text{arcsin}\left(\sqrt{\CAI_{ \r}}\right)-2\text{arcsin}\left(\sqrt{\CAI_{\ef}}\right)
\end{align*}
\]

$h^{\rr}\CAI^{|j}$:  Cohen's $h$ effect size quantifying the discrepancy between $\CAI_{\r}^{|j}$ vs. $\CAI_{\ef}^{|j}$ for the item set excluding item $j$ under PFI. 
\[
\begin{align*}
 h^{\rr}\CAI^{|j} &= 2\text{arcsin}\left(\sqrt{\CAI_{ \r}^{|j}}\right)-2\text{arcsin}\left(\sqrt{\CAI_{\ef}^{|j}}\right)
\end{align*}
\]


### Impact of removing an item on the discrepancy between  $h^{\rr}\CAI$ vs. $h^{\rr}\CAI^{|j}$

$\Delta^{|j} h^{\rr}\CAI$: Cohen's $h$ effect size quantifying the discrepancy between $h^{\rr}\CAI$ vs. $h^{\rr}\CAI^{|j}$.
In other words, the effect size of the change in bias when the $j$-th item is dropped.

\[
\begin{align*}
\Delta^{|j} h^{\rr}\CAI&= | h^{\rr}\CAI| - | h^{\rr}\CAI^{|j}|
\end{align*}
\]

## Illustrative Example: CES-D 
Example based on Zhang et al.'s 2011 examination of the Center for
Epidemiological Studies Depression (CES-D) Scale (Radloff, 1977). 

We first demonstrate the use of the item deletion indices and relevant
functions on the full four dimensional CES-D Scale, assuming that selection 
(binary classification) will be based on scores on the full scale. Then, we
demonstrate how item deletion can be performed on the scale after the deletion 
of one item. Finally, we demonstrate the use of the item deletion indices on a 
single dimensional scale by treating each subscale of the CES-D Scale as a 
separate factor, and assuming that classification decisions will be based on the
subscale scores. For all analyses, we will consider the deletion of one item
at a time. 

```{r setup, warning=FALSE, message=FALSE}
library(unbiasr)
library(lavaan)
```

```{r}
# Zhang et al. (2011) BMC Medical Research Methodology, Tables 3-4 on page 7

# Reference group: Chinese, Focal group: Dutch
pmix_CESD_r <- 4903/(1903+4903)

# Unstandardized factor loadings
lambda_SOM_r <- lambda_SOM_f <- c(1.00, 1.03, 1.18, 1.29, 1.07, 1.02, 1.26)
lambda_DEP_r <- lambda_DEP_f <- c(1.00, 1.13, 0.82, 0.91, 1.11, 0.92, 1.06)
lambda_POS_r <- lambda_POS_f <- c(1.00, 1.66, 2.30, 2.29)
lambda_INT_r <- lambda_INT_f <- c(1.00, 0.94)

# Unstandardized intercepts
nu_SOM_r <- c(0.69, 0.56, 0.78, 0.81, 0.88, 0.74, 0.70)
nu_SOM_f <- c(0.69, 0.56, 0.78, 0.80, 0.88, 0.74, 0.70)
nu_DEP_r <- c(0.52, 0.55, 0.57, 0.42, 0.57, 0.50, 0.56)
nu_DEP_f <- c(0.52, 0.55, 0.30, 0.42, 0.57, 0.50, 0.56)
nu_POS_r <- c(1.54, 1.36, 1.16, 1.08)
nu_POS_f <- c(0.68, 1.36, 1.16, 1.08)
nu_INT_r <- nu_INT_f <- c(0.44, 0.41)

# Unstandardized uniqueness
Theta_SOM_r <- Theta_SOM_f <- diag(c(0.45, 0.37, 0.39, 0.40, 0.57, 0.51, 0.37))
Theta_DEP_r <- diag(c(0.29, 0.30, 0.41, 0.31, 0.29, 0.27, 0.24))
Theta_DEP_f <- diag(c(0.29, 0.13, 0.09, 0.14, 0.29, 0.27, 0.24))
Theta_POS_r <- diag(c(1.20, 0.81, 0.32, 0.32))
Theta_POS_f <- diag(c(0.72, 0.81, 0.32, 0.32))
Theta_INT_r <- diag(c(0.19, 0.23))
Theta_INT_f <- diag(c(0.19, 0.08))

# Latent mean differences
alpha_SOM_r <- 0
alpha_DEP_r <- 0
alpha_POS_r <- 0
alpha_INT_r <- 0
alpha_SOM_f <- -0.261
alpha_DEP_f <- -0.259
alpha_POS_f <- -0.125
alpha_INT_f <- -0.323

# Latent mean variances
psi_SOM_r <- 0.482^2
psi_SOM_f <- 0.324^2
psi_DEP_r <- 0.570^2
psi_DEP_f <- 0.318^2
psi_POS_r <- 0.354^2
psi_POS_f <- 0.329^2
psi_INT_r <- 0.574^2
psi_INT_f <- 0.184^2

# Cutoff of 16/60 on full scale. 20 items, each item scored 0-3.
```

### Full 4-Factor CES-D Scale

```{r CESD_full, include=TRUE}
lambda_CESD_r <- rbind(cbind(lambda_SOM_r, rep(0, 7), rep(0, 7), rep(0, 7)),
                       cbind(rep(0, 7), lambda_DEP_r, rep(0, 7), rep(0, 7)),
                       cbind(rep(0, 4), rep(0, 4), lambda_POS_r, rep(0, 4)),
                       cbind(rep(0, 2), rep(0, 2), rep(0, 2), lambda_INT_r))
lambda_CESD_f <- rbind(cbind(lambda_SOM_f, rep(0, 7), rep(0, 7), rep(0, 7)),
                       cbind(rep(0, 7), lambda_DEP_f, rep(0, 7), rep(0, 7)),
                       cbind(rep(0, 4), rep(0, 4), lambda_POS_f, rep(0, 4)),
                       cbind(rep(0, 2), rep(0, 2), rep(0, 2), lambda_INT_f))
psi_CESD_r <- as.matrix(c(psi_SOM_r, psi_DEP_r, psi_POS_r, psi_INT_r))
psi_CESD_f <- as.matrix(c(psi_SOM_f, psi_DEP_f, psi_POS_f, psi_INT_f))
alpha_CESD_r <- as.matrix(c(alpha_SOM_r, alpha_DEP_r, alpha_POS_r, alpha_INT_r))
alpha_CESD_f <- as.matrix(c(alpha_SOM_f, alpha_DEP_f, alpha_POS_f, alpha_INT_f))

Theta_CESD_r <- diag(c(0.45, 0.37, 0.39, 0.40, 0.57, 0.51, 0.37, #SOM
                       0.29, 0.30, 0.41, 0.31, 0.29, 0.27, 0.24, #DEP
                       1.20, 0.81, 0.32, 0.32, #POS
                       0.19, 0.23 #INT
                       ))
Theta_CESD_f <- diag(c(0.45, 0.37, 0.39, 0.40, 0.57, 0.51, 0.37, #SOM
                       0.29, 0.13, 0.09, 0.14, 0.29, 0.27, 0.24, #DEP
                       0.72, 0.81, 0.32, 0.32, #POS
                       0.19, 0.08 #INT
                       ))

nu_CESD_r <- as.matrix(c(nu_SOM_r, nu_DEP_r, nu_POS_r, nu_INT_r))
nu_CESD_f <- as.matrix(c(nu_SOM_f, nu_DEP_f, nu_POS_f, nu_INT_f))

# From Miller et al. (1997) The Factor Structure of the CES-D in Two Surveys
# of Elderly Mexican Americans p.S264; the correlation matrix of latent variables
# based on the Hertzog et al. (1990) model.
corr_CESD <- matrix(c(1, .93, .58, .85,
                      .93, 1, .64, .88,
                      .58, .64, 1, .55,
                      .85, .88, .55, 1),
                    nrow = 4, ncol = 4, byrow = TRUE)
# Compute covariance matrix estimates for the focal and reference groups.
S_f <- diag(as.vector(sqrt(psi_CESD_f)))
S_r <- diag(as.vector(sqrt(psi_CESD_r)))
psi_CESD_f <- S_f %*% corr_CESD %*% S_f
psi_CESD_r <- S_r %*% corr_CESD %*% S_r


# The latent weights are specified to be proportional to the number of items
# in each subscale.

CESD_full <- item_deletion_h(cut_z = 16,
                             weights_item = c(rep(1, 20)),
                             weights_latent = c(7, 7, 4, 2),
                             alpha_r = alpha_CESD_r,
                             alpha_f = alpha_CESD_f,
                             psi_r = psi_CESD_r,
                             psi_f = psi_CESD_f,
                             lambda_r = lambda_CESD_r,
                             lambda_f = lambda_CESD_f,
                             nu_r = nu_CESD_r,
                             nu_f = nu_CESD_f,
                             Theta_r = Theta_CESD_r,
                             Theta_f = Theta_CESD_f,
                             plot_contour = FALSE,
                             n_dim = 4,
                             n_i_per_dim = c(7, 7, 4, 2),
                             pmix_ref = pmix_CESD_r)
CESD_full
```




Items 4, 9, 10, 11, 15, 19, and 20 are determined to be the biased items, and
correspond to SOM 4, DEP 2, DEP 3, DEP 4, POS 1, INT 1, and INT 2 ($effort$, 
$depressed$, $failure$, $fearful$, $good$, $dislike$). As can be seen in the
first output table, removing any of these items leads to some minor decreases 
in $\ov{\CAI}$ (lower aggregate classification accuracy), the effect size of
which is small as illustrated in the second output table.
The item the deletion of which brings the AI ratio closest to the ideal AI ratio 
of 1 is item 15, $AI^{|15}=0.977$ (from $AI=0.908$), indicating that this
item is a strong candidate for deletion. The second largest increase is 
proximity to $AI^{|j}=1$ is achieved by the deletion of item 10 (DEP 3), with
$AI^{|10}=0.930$.

The comparison of CAI for the reference group with the expected CAI for the
focal group in the next table shows that the discrepancy between $\CAI_r$ and
$\CAI_{Ef}$ becomes smallest if item 15 is deleted as $h^{\rr}\PS=0.085$ goes
down to $h^{\rr}\PS^{|15}=0.021$, $h^{\rr}\SR=-0.157$ goes up to
$h^{\rr}\SR^{|15}=-0.047$, $h^{\rr}\SE=0.141$ goes down to
$h^{\rr}\SE^{|15}=0.026$ and $h^{\rr}\SP=-0.164$ goes up to
$h^{\rr}\SP^{|15}=-0.048$. Note that we judge improvement in the difference
between $\CAI_r$ and $\CAI_{Ef}$ by the magnitude of the difference rather than
the direction. In the comparison between CAI for reference vs. Efocal groups,
the direction of the difference indicates the group that is benefiting from the
bias. We would like to minimize bias regardless of group membership, but the
signs of the indices nevertheless give valuable information about the
classification process. The 10-th item is one other item that appears to
lead to some reduction in the discrepancy between $\CAI_r$ and $\CAI_{Ef}$.
Moving on to the final table, we see that removing the 15-th item would have the
largest impact on the discrepancy between $\CAI_r$ and $\CAI_{Ef}$, followed by
the deletion of the 10-th item.

Overall, the researcher may consider deleting either the 15-th or the 10-th item
using their domain specific expertise and consulting existing literature to
choose between the two items. The output object from the call to
`item_deletion_h()` contains other tables that may aid the researcher in this
process. For instance, the outputs of `PartInv()` may be examined for the two 
item deletion scenarios:

All items retained:

```{r}
CESD_full$PartInv$partial$outputlist$full
```

Subset excluding item 15:

```{r}
CESD_full$PartInv$partial$outputlist$`|15`
```


The user can also supply a cut-off score for the delete-one scenarios instead
of letting the function compute the proportions selected under partial and 
strict invariance and using these proportions in the delete-one scenarios:

```{r}
CESD_full_with_cutoff <- item_deletion_h(cut_z = 16,
                                         weights_item = c(rep(1, 20)),
                                         weights_latent = c(7, 7, 4, 2),
                                         alpha_r = alpha_CESD_r,
                                         alpha_f = alpha_CESD_f,
                                         psi_r = psi_CESD_r,
                                         psi_f = psi_CESD_f,
                                         lambda_r = lambda_CESD_r,
                                         lambda_f = lambda_CESD_f,
                                         nu_r = nu_CESD_r,
                                         nu_f = nu_CESD_f,
                                         Theta_r = Theta_CESD_r,
                                         Theta_f = Theta_CESD_f,
                                         plot_contour = FALSE,
                                         n_dim = 4,
                                         n_i_per_dim = c(7, 7, 4, 2),
                                         pmix_ref = pmix_CESD_r,
                                         delete_one_cutoff = 16/60*(60-3))
CESD_full_with_cutoff
```

Let's assume for the sake of illustration that the researcher decides to drop
item 15 ($good$). We can repeat the process with the new item weights:

```{r}
CESD_full_drop15 <- item_deletion_h(
                          cut_z = 16/60*(60-3),
                          weights_item = c(rep(1,14), 0, rep(4/3, 3), 1, 1),
                          weights_latent = c(7, 7, 3, 2),
                          alpha_r = alpha_CESD_r,
                          alpha_f = alpha_CESD_f,
                          psi_r = psi_CESD_r,
                          psi_f = psi_CESD_f,
                          lambda_r = lambda_CESD_r,
                          lambda_f = lambda_CESD_f,
                          nu_r = nu_CESD_r,
                          nu_f = nu_CESD_f,
                          Theta_r = Theta_CESD_r,
                          Theta_f = Theta_CESD_f,
                          pmix_ref = pmix_CESD_r,
                          plot_contour = FALSE,
                          n_dim = 4,
                          n_i_per_dim = c(7, 7, 3, 2))
CESD_full_drop15
```

All items retained:

```{r}
CESD_full_drop15$PartInv$partial$outputlist$full
```

Subset excluding item 10:

```{r}
CESD_full_drop15$PartInv$partial$outputlist$`|10`
```


### CES-D Somatic Complaints Factor

```{r }
# Items: bothered, appetite, mind, effort, sleep, talk, get going
CESD_som <- item_deletion_h(cut_z = 16/60*7*3,
                            weights_item = c(rep(1,7)), 
                            weights_latent = 1,   
                            alpha_r = alpha_SOM_r,
                            alpha_f = alpha_SOM_f,
                            psi_r = psi_SOM_r,
                            psi_f = psi_SOM_f,
                            lambda_r = lambda_SOM_r,
                            lambda_f = lambda_SOM_f,
                            nu_r = nu_SOM_r,
                            nu_f = nu_SOM_f,
                            Theta_r = Theta_SOM_r, 
                            Theta_f = Theta_SOM_f,
                            pmix_ref = pmix_CESD_r,
                            plot_contour = FALSE,
                            n_dim = 1)
                              
CESD_som
```
 
The first table illustrates that removing item 4 from the Somatic Complaints 
subscale leads to a decreases in aggregate SR, aggregate SE, and aggregate SP, 
suggesting worse overall performance if this item is dropped. The third table
shows that the deletion of item 4 brings the AI ratio from the
already-high $0.998$ to $1$. Similarly, removing this item brings the
already-small difference between the reference and Efocal groups (ranging between
$-0.003$ and $0.003$) to $0$ with a very small effect size of $0.002$ to $0.003$.
These findings suggest that removing the fourth item will harm or lead to a
negligible improvement in CAI, therefore the full item set should be retained.
 

### CES-D Depressive Affect Factor

```{r  fig.width=7, fig.height=6}
# Items: blues, depressed, failure, fearful, lonely, crying, sad
CESD_dep <- item_deletion_h(cut_z = 16/60*7*3,
                            weights_item = c(rep(1,7)),
                            weights_latent = 1,  
                            alpha_r = alpha_DEP_r,
                            alpha_f = alpha_DEP_f,
                            psi_r = psi_DEP_r,
                            psi_f = psi_DEP_f,
                            lambda_r = lambda_DEP_r,
                            lambda_f = lambda_DEP_f,
                            nu_r = nu_DEP_r,
                            nu_f = nu_DEP_f,
                            Theta_r = Theta_DEP_r, 
                            Theta_f = Theta_DEP_f,
                            pmix_ref = pmix_CESD_r,  
                            plot_contour = FALSE,
                            n_dim = 1)
CESD_dep
```

`item_deletion_h` has determined items 2, 3, and 4 to contain some level of bias.
We see from the first table that $\ov{\SP}$ is around $0.940$ for all item 
deletion scenarios while $\ov{\SR}$ and $\ov{\SE}$ are slightly lower at around 
$0.815$ to $830$, suggesting that the Depressive Affect subscale is best at not
selecting the individuals who should not be selected. We see that aggregate SE,
aggregate SR, and aggregate SP for the full item set are higher than the other item 
subsets, suggesting that the removal of a biased item will likely not improve 
aggregate CAI. $h$ values in the second table range between $0.010$ to $0.045$, 
showing that the impact of removing an item will be quite small. 

The AI ratio table shows that while removing the third item increases AI from 
$0.920$ to $0.993$, bias is not fully eliminated as $AI^{|3}<1$. The removal of
either of item 2 or item 4 increases the discrepancy between the reference and 
Efocal groups. The second-to-last table illustrate that the removal of item 3
brings $h^{\rr}\CAI$ closer to 0, indicating an improvement that has a
minimal-small effect size as shown in the final table. Removing any other item 
harms CAI. 

Given the lack of agreement between indices on whether the deletion of an item 
improves or harms performance and the small effect size of the potential 
improvement, it may be best to retain all items or choose an alternative method 
to item deletion for this subscale. 


### CES-D Positive Affect Factor

```{r }
# Items: good (biased), hopeful, happy, enjoyed
CESD_pos <- item_deletion_h(cut_z = 16/60*12, 
                            weights_item = c(rep(1,4)), 
                            weights_latent = 1,
                            alpha_r = alpha_POS_r,
                            alpha_f = alpha_POS_f,
                            psi_r = psi_POS_r,
                            psi_f = psi_POS_f,
                            lambda_r = lambda_POS_r,
                            lambda_f = lambda_POS_f,
                            nu_r = nu_POS_r,
                            nu_f = nu_POS_f,
                            Theta_r = Theta_POS_r, 
                            Theta_f = Theta_POS_f,
                            pmix_ref = pmix_CESD_r, 
                            plot_contour = FALSE,
                            user_specified_items = c(1:4))
CESD_pos
```
 
The only biased item in the Positive Affect subscale is item 1. We see from the 
first output table that deleting the first item increases $\ov{\SR}$ and 
$\ov{\SE}$ from $0.883$ to $0.894$, and $\ov{\SP}$ from $0.752$ to $0.777$. The
second output table shows that $h^{|1}\ov{\SR}=h^{|1}\ov{\SE}=-0.037$ and
$h^{|1}\ov{\SP}=-0.059$, which suggests that the improvement in all three 
$\CAI$ have a small effect size $(h < .20)$.

The AI ratio when the full item set is used is $0.87$. Removing the first item 
achieves an AI ratio of $1$, suggesting that the proportion selected for the 
reference group is equal to that which would have been selected for the focal 
group if the focal and reference groups both followed the reference group's 
latent score distribution (i.e., if they were matched on their true (lack of) 
positive affect). This finding shows that removing the first item eliminates
measurement bias, and is replicated in the next table comparing $\CAI_R$ with 
$\CAI_{Ef}$ where $h^{\rr}\SR^{|1}=h^{\rr}\SE^{|1}=h^{\rr}\SP^{|1}=0$. Put into 
words, if item 1 is removed, PS, SR, SE, and SP for the reference group equal
the expected PS, SR, SE, and SP for the focal group. 

The final table shows that the effect size of removing the first item on the 
difference between the reference group's CAI and the focal group's expected CAI
is largest for SE with $\Delta^{|1} h^{\rr}\SE=0.223$ and SR with
$\Delta^{|1} h^{\rr}\SP=0.368$, corresponding to small-medium effect sizes. 

Taken together, these improvements and the lack of any decreases in CAI suggests 
that the researcher may drop this item barring any domain specific reasons not 
to do so.
 
### CES-D Interpersonal Problems Factor

```{r}
# Items: unfriendly, dislike
CESD_int <- item_deletion_h(cut_z = 16/60*2*3,
                            weights_item = c(rep(1,2)),
                            weights_latent = 1, 
                            alpha_r = alpha_INT_r,
                            alpha_f = alpha_INT_f,
                            psi_r = psi_INT_r,
                            psi_f = psi_INT_f,
                            lambda_r = lambda_INT_r,
                            lambda_f = lambda_INT_f,
                            nu_r = nu_INT_r,
                            nu_f = nu_INT_f,
                            Theta_r = Theta_INT_r, 
                            Theta_f = Theta_INT_f,
                            pmix_ref = pmix_CESD_r,
                            plot_contour = FALSE,
                            n_dim = 1)
CESD_int
```
 
Removing the second item in this 2-item subscale leads to lower $\ov{\CAI}$, and 
the effect size of this decrease is $h^{|2} \ov{\SR}= h^{|2}\ov{\SE}=0.173$, which
corresponds to a worsening performance with a small effect size. The adverse 
impact ratio goes up to $1$ from $0.966$ and $h^{\rr}\CAI^{|2}=0$ for all
indices. The effect size of the improvement in the discrepancy between the
reference and Efocal groups on SR whenitem 2 is deleted is
$\Delta^{|2} h^{\rr}\SR=0.132$, $\Delta^{|2} h^{\rr}\SE=0.062$, and 
$\Delta^{|2} h^{\rr}\SE=0.086$.
Given these conflicting findings and the fact that this subscale only has two
items, it would be best to retain both items if the subscale will be used on its 
own to make classification decisions.

Now to illustrate the use of `user_specified_items`:

```{r }
CESD_pos <- item_deletion_h(cut_z = 16/60*12, 
                            weights_item = c(rep(1, 4)), 
                            weights_latent = 1,
                            alpha_r = alpha_POS_r,
                            alpha_f = alpha_POS_f,
                            psi_r = psi_POS_r,
                            psi_f = psi_POS_f,
                            lambda_r = lambda_POS_r,
                            lambda_f = lambda_POS_f,
                            nu_r = nu_POS_r,
                            nu_f = nu_POS_f,
                            Theta_r = Theta_POS_r, 
                            Theta_f = Theta_POS_f,
                            pmix_ref = pmix_CESD_r, 
                            plot_contour = FALSE,
                            user_specified_items = c(1:3))
CESD_pos
```

Specifying `plot_contour = TRUE`:

```{r fig.width=7, fig.height=6}
CESD_pos <- item_deletion_h(cut_z = 16/60*12, 
                            weights_item = c(rep(1,4)), 
                            weights_latent = 1,
                            alpha_r = alpha_POS_r,
                            alpha_f = alpha_POS_f,
                            psi_r = psi_POS_r,
                            psi_f = psi_POS_f,
                            lambda_r = lambda_POS_r,
                            lambda_f = lambda_POS_f,
                            nu_r = nu_POS_r,
                            nu_f = nu_POS_f,
                            Theta_r = Theta_POS_r, 
                            Theta_f = Theta_POS_f,
                            pmix_ref = pmix_CESD_r, 
                            plot_contour = TRUE)
```

Using the `summary()` function:


```{r }
CESD_pos <- item_deletion_h(cut_z = 16/60*12, 
                            weights_item = c(rep(1, 4)), 
                            weights_latent = 1,
                            alpha_r = alpha_POS_r,
                            alpha_f = alpha_POS_f,
                            psi_r = psi_POS_r,
                            psi_f = psi_POS_f,
                            lambda_r = lambda_POS_r,
                            lambda_f = lambda_POS_f,
                            nu_r = nu_POS_r,
                            nu_f = nu_POS_f,
                            Theta_r = Theta_POS_r, 
                            Theta_f = Theta_POS_f,
                            pmix_ref = pmix_CESD_r, 
                            plot_contour = FALSE)
summary(CESD_pos)
```
